### 2022-10-01 chapters/programming_languages/rpc/rpc.tex
add : correlation table
update : typos in thechempower
add : rpc comclusion

\begin{figure}[!hbt]
    \begin{center}
        \includegraphics[width=1.2\linewidth]{imgs/rps_clients}
    \end{center}
    \caption{Number of requests per second based on the number of clients}\label{fig:rps_clients}
\end{figure}
%  TODO : REname the frameworks based on their dockerfile 
Figure~\ref{fig:rps_clients} presents the number of requests per second for each implementation. The heatmap is colored in a logarithmic scale to visualize the results better.
As one can observe, most of the servers hit their RPS limit after five clients and 100 clients for VM-based servers, and after this, the number keeps constant, decreasing the average RPS per client.
.Net server is the most performant, followed by Java and Go, while Python and Ruby are the least performant.

@@

\paragraph{Synthesis}: 
Depending on the number of clients, most frameworks exhibit two distinct behaviors. When dealing with a small number of clients, frameworks, regardless of programming category, tend to be energy-efficient and performant.
However, as the number of clients grows, the frameworks become more energy-hungry and less performant. Interpreted languages suffer the most, particularly in terms of latency and the cost of a single request.
\textsf{Crystal}, interestingly, acted. It behaves oppositely. The cost of a single request increases as the number of clients decreases.

@@

@@

\input{correlation_table.tex}

@@

\subsection{Conclusion \note{missing}}

>>>>

\begin{figure}[!hbt]
    \begin{center}
        \includegraphics[width=1.2\linewidth]{imgs/rps_clients}
    \end{center}
    \caption{Number of requests per second based on the number of clients}\label{fig:rps_clients}
\end{figure}
%  TODO : REname the frameworks based on their dockerfile

Figure~\ref{fig:rps_clients} presents the number of requests per second for each implementation. The heatmap is colored in a logarithmic scale to visualize the results better.
As one can observe, most of the servers hit their RPS limit after five clients and 100 clients for VM-based servers, and after this, the number keeps constant, decreasing the average RPS per client.
.Net server is the most performant, followed by Java and Go, while Python and Ruby are the least performant.

@@

% \paragraph{Synthesis}:
% Depending on the number of clients, most frameworks exhibit two distinct behaviors. When dealing with a small number of clients, frameworks, regardless of programming category, tend to be energy-efficient and performant.
% However, as the number of clients grows, the frameworks become more energy-hungry and less performant. Interpreted languages suffer the most, particularly in terms of latency and the cost of a single request.
% \textsf{Crystal}, interestingly, acted. It behaves oppositely. The cost of a single request increases as the number of clients decreases.

@@

% NOTE : discuss this with Romain later (90% chances that it is not needed)
% \paragraph{overall analysis}
% \input{correlation_table.tex}
% in order to reduce the space of research, we processed to do a correlation test between the different variables. We used the Pearson Spearman rank correlation~\cite{zar2005spearman}.

% Table~\ref{table:correlation} presents the correlation between the different observable variables. As one can see,  There is a high correlation between the number of requests, the 99\% tail latency, and the average energy cost. This means that the more requests are answered, the less energy is consumed, and the more latency is observed. However, the correlation between the average power consumption and the other variables is low, which means that the power consumption is not directly related to the other variables.  
% As one can see, except for rust-based implementation, the correlation between the energy consumption per request and the tail latency was extremely high. 
% Therefore we will focus on two main variables 
% \begin{itemize}
%     \item average power consumption - that will represent the energetic behavior of the server 
%     \item average request per second: that will be our representative variable to estimate the performance 
% \end{itemize}

% We chose these two variables because they are both expressed in seconds, which will narrow our analysis to the present behavior of the server at any given time and not along the whole execution process.

% As one can notice in the first column of table~\ref{table:correlation}
% There are three main categories of servers. 
% \begin{enumerate}
%     \item Positive correlation between the energy and performance :  
% \end{enumerate}

% \paragraph{metric based analysis}

@@

@@

\subsection{Conclusion}

This section presents a study on the impact of programming languages on the energy for request handling. To do that, we used an implementation of 25 frameworks based on 17 programming languages. 
These servers use the official RPC protocol, reducing programmers' bias toward specific languages.

The results show that the number of clients had a binary effect on the servers. 
With a small number of clients, there was no typical behavior between different categories. On the other hand, when dealing with a more significant number of clients,  interpreted languages and compiled ones dropped in terms of performance while keeping the same average power, unlike the Vm~based ones that increased their average power while keeping the same performances. Overall the second strategy had a better impact on the single request cost than the first one.

As for the evolution of the query size, we have seen three modes of behavior for each framework, depending on the size of the requests: the stress-free mode, the escalation mode, and the broken state mode. 
We start with the stress-free mode. The leader class was the compiled languages, while the VM-based ones tended to consume more energy. 
Finally, with the escalation mode. one could observe three strategies to deal with the increase in request size. The first strategy was to drop in performance while keeping the same power; the second was to increase the average power consumption without impacting the performance; the third was a combination of both previous strategies with an increase in power and a drop in performance. Interestingly the third strategy had a lower cost per request than the first one. 
Finally, most implementations could not handle requests heavier than 10 MB for the broken mode. Elixir was an exception to this limit despite its low performance compared to other languages

This study shows the absence of a universal language when dealing with RPC requests. Moreover, each implementation had a different way of dealing with scalability. While some chose to increase the average power consumption, others dropped in performance. Both of these strategies led to a higher cost of a single request.
